### 2017-05-06 paper/evaluation.tex
Adjusted table

%% Table header macros
\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1x & #2\%}

\begin{figure*}[t]
\centering
\small
\begin{tabular}{lccccccccccc}
\toprule
\multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
Choco Solver & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%

>>>>

%% Table header macros
\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1 & #2}

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|rr|rrrrrrrrrr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
OpenMRS Core (\CodeIn{api})           & \entry{13.8m}{X} & \entry{-}{58.07\%} & \entry{1.86x}{65.55\%} & \entry{2.01x}{61.56\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Apache Flume (\CodeIn{core}) & \entry{8.3m}{Y} & \entry{2.82x}{18.11\%} & \entry{-}{0\%} & \entry{2.78x}{16.84\%} & \entry{-}{0\%} & \entry{2.87x}{18.88\%}\\%
Apache Giraph (\CodeIn{core})  & \entry{7m}{Z} & \entry{2.08x}{5.08\%} & \colheader{\cellcolor{lightgray}JVM Crash}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Struct (\CodeIn{rest})  & \entry{Xm}{Z} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
